Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-06 paper/ms.tex
correcting a small typo

Summarizing, the median mass could be anything in the range
$10^{9.5}$\hMsun and $10^{11.5}$ (a $2.0$ dex range), but the width is
highly constrained to be between $0.2$ and $0.6$ dex.

>>>>

Summarizing, the median mass could be anything in the range
$10^{9.5}$\hMsun\ and $10^{11.5}$\hMsun\ (a $2.0$ dex range), but the width is
highly constrained to be between $0.2$ and $0.6$ dex.
